prod_prep_mergedata

### 2024-01-26 production/prod_analysis.Rmd
reorder contextual effects

# generate analytical sample
df_study1 <- 
  df_study1_long_comunas %>%
  select(idencuesta,ola,comuna,just_educ:merit_talent, ahead_family:sexo, ginilag22_17, gini_ypch_2022, gini_ypch, prop_univ, gini_gc, prop_pagado, pagadlag22_16=pagadolag22_16, total_mat_pagado, var_simce_comuna_rescaled, prom_simce_comuna_rescaled, univlag22_17) %>% 
  na.omit() %>% 
  mutate(ola=as.factor(ola),
         sexo=as.factor(sexo)
         )
# Hipotesis
h1 <- "ola"
h2 <- "ola+merit_effort+merit_talent"
h3 <- "ola+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family"
h4 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family"
h5 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo"

h6 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17"
h7 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_univ+univlag22_17"
h8 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17"
h9 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_pagado+pagadlag22_16"
h10 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"
h11 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"

hfull <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"

# A. Education distributive justice
educ.null <- lmer(formula(paste0("just_educ~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
educ1 <- lmer(formula(paste0("just_educ~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ2 <- lmer(formula(paste0("just_educ~",h2,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ3 <- lmer(formula(paste0("just_educ~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ4 <- lmer(formula(paste0("just_educ~",h4,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ5 <- lmer(formula(paste0("just_educ~",h5,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ6 <- lmer(formula(paste0("just_educ~",h6,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ7 <- lmer(formula(paste0("just_educ~",h7,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ8 <- lmer(formula(paste0("just_educ~",h8,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ9 <- lmer(formula(paste0("just_educ~",h9,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ10 <- lmer(formula(paste0("just_educ~",h10,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ11 <- lmer(formula(paste0("just_educ~",h11,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ12 <- lmer(formula(paste0("just_educ~",hfull,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

@@

```{r}
# table 2: contextuales
omit <- "(ola)|(merit_effort)|(merit_talent)|(ahead_hardwork)|(ahead_educ)|(ahead_ambition)|(ahead_family)|(educ)|(quintil1)|(ess)|(pos_id)|(edad)|(sexo)|(Intercept)"
texreg::htmlreg(list(educ6, educ7,educ8,educ9,educ10,educ11,educ12),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05", 
                omit.coef = omit,
                custom.coef.names = c(
                                      "Gini comunal",
                                      "Cambio gini 2022-2017",
                                      "Proporción educ universitaria",
                                      "Cambio prop. universitaria 2022-2017",
                                      "Proporción matrícula privada",
                                      "Cambio matrícula privada 2022-2016",
                                      "Promedio Simce comuna",
                                      "Varianza Simce comuna"),
                file = "output/tables/table2-contextual.html")
          #omit.coef = omit

@@

# generate analytical sample
df_study1 <- 
  df_study1_long_comunas %>%
  select(idencuesta,ola,comuna,just_educ:merit_talent, ahead_family:sexo, ginilag22_17, gini_ypch_2022, gini_ypch, prop_univ, gini_gc, prop_pagado, pagadlag22_16=pagadolag22_16, total_mat_pagado, var_simce_comuna_rescaled, prom_simce_comuna_rescaled, univlag22_17) %>% 
  na.omit() %>% 
  mutate(ola=as.numeric(ola),
         sexo=as.factor(sexo)
         )
# Hipotesis
h1b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"
h2b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*merit_effort"
h3b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*merit_talent"
h4b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_hardwork"
h5b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_educ"
h6b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_ambition"
h7b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_family"

@@

# table 3: interacciones
texreg::htmlreg(list(educ1, educ2,educ3,educ4,educ5,educ6,educ7),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05", 
                custom.coef.names = c("Intercepto",
                                      "ola",
                                      "Merito: esfuerzo",
                                      "Merito: Inteligencia",
                                      "Goahead: trabajo duro",
                                      "Goahead: educacion",
                                      "Goahead: ambicion",
                                      "Goahead: Familia",
                                      "Ed. media <br> <i>(Ref. Ed. básica)</i>",
                                      "Ed. técnica",
                                      "Ed. universitaria",
                                      "Quintil 2 <br> <i>(Ref. Quintil 1)</i>",
                                      "Quintil 3",
                                      "Quintil 4",
                                      "Quintil 5",
                                      "Quintil NA",
                                      "Estatus social subjetivo",
                                      "Pos. política: Centro <br> <i>(Ref. izquierda)</i>",
                                      "Pos. política: Derecha",
                                      "Pos. política: No se identifica",
                                      "Edad 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Edad 50-64",
                                      "Edad 65 o más",
                                      "Mujer <br> <i>(Ref. Hombre)</i>",
                                      "Gini comunal",
                                      "Cambio gini 2022-2017",
                                      "Proporción educ universitaria",
                                      "Cambio prop. universitaria 2022-2017",
                                      "Proporción matrícula privada",
                                      "Cambio matrícula privada 2022-2016",
                                      "Promedio Simce comuna",
                                      "Varianza Simce comuna",
                                      "ola*merit:esfuerzo",
                                      "ola*merit:talento",
                                      "ola*goahead:hardwork",
                                      "ola*goahead:educ",
                                      "ola*goahead:ambition",
                                      "ola*goahead:family"),
                file = "output/tables/table3-interac.html")
          #omit.coef = omit

webshot2::webshot(url ="output/tables/table3-interac.html" ,file ="output/tables/table3-interac.png")
```

>>>>

# generate analytical sample
df_study1 <- 
  df_study1_long_comunas %>%
  select(idencuesta,ola,comuna,just_educ:merit_talent, ahead_family:sexo, ginilag22_17, gini_ypch_2022, gini_ypch, prop_univ, gini_gc, prop_pagado, pagadlag22_16=pagadolag22_16, total_mat_pagado, var_simce_comuna_rescaled, prom_simce_comuna_rescaled, univlag22_17, loginc_mean, logincomelag22_17) %>% 
  na.omit() %>% 
  mutate(ola=as.factor(ola),
         sexo=as.factor(sexo)
         )
# Hipotesis
h1 <- "ola"
h2 <- "ola+merit_effort+merit_talent"
h3 <- "ola+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family"
h4 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family"
h5 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo"

h6 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17"
h7 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_univ+univlag22_17"
h8 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17"
h9 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_pagado+pagadlag22_16"
h10 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"
h11 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"
h12 <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+loginc_mean+logincomelag22_17"

hfull <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+loginc_mean+logincomelag22_17"

# A. Education distributive justice
educ.null <- lmer(formula(paste0("just_educ~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
educ1 <- lmer(formula(paste0("just_educ~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ2 <- lmer(formula(paste0("just_educ~",h2,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ3 <- lmer(formula(paste0("just_educ~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ4 <- lmer(formula(paste0("just_educ~",h4,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ5 <- lmer(formula(paste0("just_educ~",h5,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ6 <- lmer(formula(paste0("just_educ~",h6,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ7 <- lmer(formula(paste0("just_educ~",h7,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ8 <- lmer(formula(paste0("just_educ~",h8,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ9 <- lmer(formula(paste0("just_educ~",h9,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ10 <- lmer(formula(paste0("just_educ~",h10,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ11 <- lmer(formula(paste0("just_educ~",h11,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ12 <- lmer(formula(paste0("just_educ~",h12,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
educ13 <- lmer(formula(paste0("just_educ~",hfull,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

@@

```{r}
# table 2: contextuales
omit <- "(ola)|(merit_effort)|(merit_talent)|(ahead_hardwork)|(ahead_educ)|(ahead_ambition)|(ahead_family)|(educ)|(quintil1)|(ess)|(pos_id)|(edad)|(sexo)|(Intercept)"
texreg::htmlreg(list(educ6, educ7,educ8,educ9,educ10,educ11,educ12,educ13),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05", 
                omit.coef = omit,
                custom.coef.names = c(
                                      "Gini comunal",
                                      "Cambio gini 2022-2017",
                                      "Proporción educ universitaria",
                                      "Cambio prop. universitaria 2022-2017",
                                      "Proporción matrícula privada",
                                      "Cambio matrícula privada 2022-2016",
                                      "Promedio Simce comuna",
                                      "Varianza Simce comuna",
                                      "Ingreso comunal",
                                      "Cambio ingreso comunal 2022-2017"),
                file = "output/tables/table2-contextual.html")
          #omit.coef = omit

@@

# generate analytical sample
df_study1 <- 
  df_study1_long_comunas %>%
  select(idencuesta,ola,comuna,just_educ:merit_talent, ahead_family:sexo, ginilag22_17, gini_ypch_2022, gini_ypch, prop_univ, gini_gc, prop_pagado, pagadlag22_16=pagadolag22_16, total_mat_pagado, var_simce_comuna_rescaled, prom_simce_comuna_rescaled, univlag22_17) %>% 
  na.omit() %>% 
  mutate(ola=as.factor(ola),
         sexo=as.factor(sexo)
         )
# Hipotesis
h1b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled"
h2b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*merit_effort"
h3b <- "merit_effort+merit_talent+ola+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+merit_talent*ola"
h4b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_hardwork"
h5b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_educ"
h6b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_ambition"
h7b <- "ola+merit_effort+merit_talent+ahead_hardwork+ahead_educ+ahead_ambition+ahead_family+educ+quintil1+ess+pos_id+edad+sexo+gini_ypch+ginilag22_17+prop_univ+univlag22_17+prop_pagado+pagadlag22_16+prom_simce_comuna_rescaled+var_simce_comuna_rescaled+ola*ahead_family"

@@

# table 3: interacciones
texreg::knitreg(list(educ1, educ2,educ3,educ4,educ5,educ6,educ7),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05", 
                custom.coef.names = c("Intercepto",
                                      "2017",
                                      "2018",
                                      "2019",
                                      "2022",
                                      "Merito: esfuerzo",
                                      "Merito: Inteligencia",
                                      "Goahead: trabajo duro",
                                      "Goahead: educacion",
                                      "Goahead: ambicion",
                                      "Goahead: Familia",
                                      "Ed. media <br> <i>(Ref. Ed. básica)</i>",
                                      "Ed. técnica",
                                      "Ed. universitaria",
                                      "Quintil 2 <br> <i>(Ref. Quintil 1)</i>",
                                      "Quintil 3",
                                      "Quintil 4",
                                      "Quintil 5",
                                      "Quintil NA",
                                      "Estatus social subjetivo",
                                      "Pos. política: Centro <br> <i>(Ref. izquierda)</i>",
                                      "Pos. política: Derecha",
                                      "Pos. política: No se identifica",
                                      "Edad 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Edad 50-64",
                                      "Edad 65 o más",
                                      "Mujer <br> <i>(Ref. Hombre)</i>",
                                      "Gini comunal",
                                      "Cambio gini 2022-2017",
                                      "Proporción educ universitaria",
                                      "Cambio prop. universitaria 2022-2017",
                                      "Proporción matrícula privada",
                                      "Cambio matrícula privada 2022-2016",
                                      "Promedio Simce comuna",
                                      "Varianza Simce comuna",
                                      "ola*merit:esfuerzo",
                                      "ola*merit:talento",
                                      "ola*goahead:hardwork",
                                      "ola*goahead:educ",
                                      "ola*goahead:ambition",
                                      "ola*goahead:family"),
                file = "output/tables/table3-interac.html")
          #omit.coef = omit

webshot2::webshot(url ="output/tables/table3-interac.html" ,file ="output/tables/table3-interac.png")

## graph interact
#sjPlot::plot_model(educ2, type = "int", mdrt.values = "meansd")
#predit<-interplot::interplot(m = educ2,var1 = "merit_effort",var2 = "ola",point = T)
#predit$data[c(1,2,4,6,8),]
#predit$data[c(1,2,4,6,8),] %>% ggplot2::ggplot() %>%
```

### 2024-01-26 production/prod_prep-mergedata.Rmd
reorder contextual effects

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long_comunas,
                  y = select(df_gini_comunas_long, comunacod=COMUNA_COD,year, starts_with("gini"),prop_univ), 
                  by = c("comunacod", "year"))

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long_comunas,
                  y = select(df_gini_comunas_wide, comunacod,starts_with("gini"), starts_with("prop_univ"), starts_with("univlag")), 
                  by = c("comunacod"))

>>>>

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long_comunas,
                  y = select(df_gini_comunas_long, comunacod=COMUNA_COD,year, starts_with("gini"), prop_univ, starts_with("inc"), starts_with("log")), 
                  by = c("comunacod", "year"))

df_study1_long_comunas <- 
 dplyr::left_join(x = df_study1_long_comunas,
                  y = select(df_gini_comunas_wide, comunacod,starts_with("gini"), starts_with("prop_univ"), starts_with("univlag"), starts_with("inc"), starts_with("log")), 
                  by = c("comunacod"))
